---
title: "Teaching Marketing Analytics: A Pricing Exercise for Quantitative and Substantive Marketing Skills"
author: "Authors anonymized for peer review"
output:
  html_notebook:
    theme: united
    toc: yes
    toc_float: no
    toc_depth: 3
    number_sections: no
editor_options:
  markdown:
    wrap: 72
---

```{r setup, echo=FALSE}
options(scipen = 999)
```

Your B2B firm sells an energy-efficient heater fan and has divided the
country into 100 comparable sales territories, each staffed exclusively
by a female sales representative. The sales representatives differ
according to their professional experience (measured by the number of
years they have been in sales) and whether they have an engineering
degree.

The management recently stated that 50% of the sales representatives
have at least five years of professional experience in sales, and at
least one-third of the sales representatives also have an engineering
degree.

The firm's management randomly varied the prices across the sales
territories.

In addition, the management commissioned an advertising agency to
support the sales representatives through marketing and provided a
dedicated budget. The agency should use this marketing budget for
telephone marketing and social media marketing, with an approximately
equal allocation towards the two channels (i.e., 50% phone calls and 50%
social media marketing). So far, the firm's management has randomly
varied the agency's budget across the sales territories.

The variable cost per unit of a heater fan is \$200.

In the file `data_sales.csv`, you receive information that helps you
answer the questions. The data set includes 100 rows, each describing
one of the 100 sales territories with the following variables:

+---------------------+----------------------------------------+
| Variable            | Description                            |
+:====================+:=======================================+
| `quantity`          | Number of sold heater fans in the      |
|                     | respective sales territory.            |
+---------------------+----------------------------------------+
| `price`             | Price of the heater fan sold in the    |
|                     | respective sales territory.            |
+---------------------+----------------------------------------+
| `experience`        | Number of years the sales              |
|                     | representative has been working in     |
|                     | sales.                                 |
+---------------------+----------------------------------------+
| `engineer`          | Binary variable indicating whether the |
|                     | sales representative has an            |
|                     | engineering degree (= 1) or not (= 0). |
+---------------------+----------------------------------------+
| `gender`            | Gender of the sales representative,    |
|                     | female (= 1) or other (= 0).           |
+---------------------+----------------------------------------+
| `location`          | Number of letters of the sales         |
|                     | representative's birthplace (e.g., 7   |
|                     | if the birthplace is "Chicago").       |
+---------------------+----------------------------------------+
| `budget_agency`     | Budget used by the advertising agency, |
|                     | which is either spent for phone or     |
|                     | social media marketing, in \$.         |
+---------------------+----------------------------------------+
| `budget_phone`      | Budget used for telephone marketing,   |
|                     | in \$.                                 |
+---------------------+----------------------------------------+
| `b                  | Budget used for social media           |
| udget_social_media` | marketing, in \$.                      |
+---------------------+----------------------------------------+

: Table 1: Description of the Data Set `data_sales.csv`

## 1) Exploratory Data Analysis

*For each part of this first exercise, please answer the question by
analyzing the data set through one visualization and one non-visual
descriptive analysis.*

*We do not require custom labels for the visualizations.*

### a)

Does the firm only employ female sales representatives? (2 points)

#### Solution

```{r}
df <- read.csv("data_sales.csv")
```

```{r}
summary(df$gender)
barplot(table(df$gender), main = "Barplot of Gender", xlab = "Gender", ylab = "Number of Sales Territories")
```

Yes, because the summary statistics and the barplot show that the data
set only includes `gender = 1`, corresponding to females.

### b)

Do the prices differ across sales territories? (2 points)

#### Solution

```{r}
summary(df$price)
hist(df$price, main = "Histogram of Price", xlab = "Price (in $)", ylab = "Number of Sales Territories")
```

Yes, prices differ across sales territories. For example, the summary
statistics exhibit different values for the minimum (\$209.4) and
maximum (\$369.4). Additionally, the histogram shows that prices vary
across sales territories.

### c)

Is the management's statement regarding the professional experience of
their sales representatives correct? (2 points)

#### Solution

*Statement to check: Median experience is 5 years*

```{r}
median(df$experience)
boxplot(df$experience, main = "Boxplot of Experience", ylab = "Years")
```

No, because the summary statistics and the boxplot show that the median
of `experience` is 4. If management's statement ("50% of the sales
representatives have at least five years of professional experience in
sales") were true, then the median of `experience` should be 5.

An alternative and equally correct solution is to count the observations
that have less than 5 years of experience:

```{r}
table(df$experience)
sum(df$experience >= 5) / nrow(df)
barplot(table(df$experience), main = "Barplot of Experience", xlab = "Years", ylab = "Number of Sales Territories")
```

### d)

Is the management's statement regarding the background of their sales
representatives correct? (2 points)

#### Solution

*Statement to check: At least one-third of sales representatives hold an
engineering degree.*

```{r}
table(df$engineer)
barplot(table(df$engineer), main = "Barplot of Engineering", ylab = "Number of Sales Territories")
```

Management's statement is incorrect because we only observe that 28 % of
sales representatives hold an engineering degree, not at least 33%.

$\frac{28}{72 + 28} = 0.28 < \frac{1}{3} \approx 33\%$.

### e)

Does the advertising agency's budget differ across the sales
territories? (2 points)

#### Solution

```{r}
summary(df$budget_agency)
hist(df$budget_agency, main = "Histogram of Budget Agency", xlab = "Budget in $", ylab = "Number of Sales Territories")
```

Yes, the budgets differ. The summary statistics outline that the minimum
budget across all sales territories is 329, and the maximum is 2,056.
Additionally, the histogram shows that the budget varies strongly across
sales territories.

### f)

Did the advertising agency achieve the aim of approximately equally
allocating the budget to the two channels (telephone and social media
marketing)? (2 points)

#### Solution

```{r}
cor(df$budget_phone, df$budget_social_media)
plot(df$budget_social_media, df$budget_phone, main = "Scatterplot of Budgets", xlab = "Social Media ($)", ylab = "Telephone ($)")
```

Yes, all sales territories received almost equal telephone and social
media marketing budgets. This insight is easiest to observe in the
scatterplot. The visualization displays the almost perfect linear
relationship and shows that the social media budget approximately equals
the telephone marketing budget. The correlation coefficient is almost 1,
and both budgets' average values are also almost equal.

**Note:** Displaying the individual distributions of the two variables,
e.g., via a histogram, is insufficient because a similar distribution of
two variables is a necessary but not a sufficient condition for similar
budgets in all sales territories.

### g)

Were the sales representatives born in at least 8 different cities? (2
points)

#### Solution

```{r}
nrow(table(df$location))
barplot(table(df$location), main = "Barplot of Location", xlab = "Number of Characters in City Name", ylab = "Number of Sales Territories")
```

Yes, because the data set includes 11 different values of `location`,
which implies that the sales representatives were born in *at least* 11
cities.

+-------------+-------------+-------------+-------------+
| Step        | Task        | Max. Points | Achieved    |
|             |             |             | Points      |
+:============+:============+:============+:============+
| 1-a         | Correct     | 2           |             |
|             | vi          |             |             |
|             | sualization |             |             |
|             | (1 point),  |             |             |
|             | correct     |             |             |
|             | non-visual  |             |             |
|             | descriptive |             |             |
|             | statistic   |             |             |
|             | (1 point).  |             |             |
+-------------+-------------+-------------+-------------+
| 1-b         | see above   | 2           |             |
+-------------+-------------+-------------+-------------+
| 1-c         | see above   | 2           |             |
+-------------+-------------+-------------+-------------+
| 1-d         | see above   | 2           |             |
+-------------+-------------+-------------+-------------+
| 1-e         | see above   | 2           |             |
+-------------+-------------+-------------+-------------+
| 1-f         | see above   | 2           |             |
+-------------+-------------+-------------+-------------+
| 1-g         | see above   | 2           |             |
+-------------+-------------+-------------+-------------+

## 2) Estimating a Demand Function

Estimate a linear demand function. Justify which variables you include
and which ones you ignore. Discuss the influence of price and
professional experience on the quantity and how confident you are about
their influence. (14 points)

#### Solution

##### **Step 1:** Identify the variables to include in the linear regression equation.

Include all variables except:

-   `gender`, because it only has the value 1 and, thus, no variation.
-   `location`, because there is no plausible reason why the character
    length of the sales representative's city of birth should impact
    sales.
-   `budget_phone` and `budget_social_media`, because
    -   the two variables are almost perfectly collinear (50% share each
        and correlation is almost 1), and

    -   the sum of both variables is a linear combination corresponding
        to the third variable `budget_agency`, leading to perfect
        multicollinearity:
        `budget_agency = budget_phone + budget_social_media`.

##### **Step 2: Use a linear regression to estimate** the linear demand function

###### Most Suitable Model

```{r, warning=FALSE, message=FALSE}
reg_model_1 <- lm(quantity ~ price + experience + engineer + budget_agency, data = df)
```

###### Acceptable Models

```{r, warning=FALSE, message=FALSE}
reg_model_2 <- lm(quantity ~ price + experience + engineer + budget_phone, data = df)
reg_model_3 <- lm(quantity ~ price + experience + engineer + budget_social_media, data = df)

library(stargazer)
stargazer(reg_model_1, reg_model_2, reg_model_3, type = "text", header = FALSE)
```

###### Incorrect Models

```{r, warning=FALSE, message=FALSE}
# Including two out of three variables `budget_agency`, `budget_phone`, and `budget_social_media`
reg_model_4 <- lm(quantity ~ price + experience + engineer + budget_phone + budget_social_media,
               data = df)

# Including all three multicollinear independent variables `budget_agency`, `budget_phone`, and `budget_social_media`
reg_model_5 <- lm(quantity ~ price + experience + engineer + budget_agency + budget_phone + budget_social_media,
               data = df)

stargazer(reg_model_4, reg_model_5, type = "text", header = FALSE, column.labels = c("(4)", "(5)"), model.numbers = FALSE)
```

*Notes concerning model selection:*

Model 1 is the preferred model according to the justification from
Step 1. In the incorrect model 4, we see the effects of collinearity
between the two variables `budget_phone` and `budget_social_media` (as
observed through their correlation, which is very close to 1) on the
estimated coefficients. The coefficients in model 4 have different
signs, even though the overall effect (model 1) and the effect of each
variable alone in models 2 and 3 are positive. Additionally, the sum of
the coefficients of the variables `budget_phone` and
`budget_social_media` in model 4 is similar in magnitude to the total
effect, i.e., the coefficient of the variable `budget_agency` in model
1.

##### **Step 3:** Interpretation of Model 1

If the price increases by \$1, the (expected) quantity decreases by
2.954 units.

For each additional year of work experience, the (expected) quantity
increases by 9.034 units.

Both coefficients display *p*-values smaller than 1%. Hence, we are very
confident that we can reject the null hypothesis that the coefficient is
not different from zero. Formulated differently, we are confident that
the estimated effects differ from zero.

+--------------+--------------+--------------+--------------+
| Step         | Task         | Max. Points  | Achieved     |
|              |              |              | Points       |
+==============+==============+==============+==============+
| 2-1          | Correct      | 6            |              |
|              | justification| (6 Points    |              |
|              | of which     | for the      |              |
|              | dependent    | correct      |              |
|              | and          | model. 1     |              |
|              | independent  | point        |              |
|              | variables to | deduction    |              |
|              | include in   | for each     |              |
|              | the linear   | incorrectly  |              |
|              | regression.  | included or  |              |
|              |              | excluded     |              |
|              |              | variable.    |              |
|              |              | 0.5 points   |              |
|              |              | deduction if |              |
|              |              | the correct  |              |
|              |              | decision but |              |
|              |              | not          |              |
|              |              | justified.)  |              |
+--------------+--------------+--------------+--------------+
| 2-2          | Estimate     | 2            |              |
|              | regression   |              |              |
|              | with `lm()`  |              |              |
|              | and print    |              |              |
|              | `summary()`. |              |              |
+--------------+--------------+--------------+--------------+
| 2-3          | Interpret    | 3            |              |
|              | the          |              |              |
|              | estimated    | (1.5 points  |              |
|              | coefficient  | for          |              |
|              | of `price`   | magnitude    |              |
|              | correctly.   | and          |              |
|              |              | statistical  |              |
|              |              | s            |              |
|              |              | ignificance, |              |
|              |              | each)        |              |
+--------------+--------------+--------------+--------------+
| 2-4          | Interpret    | 3            |              |
|              | the          |              |              |
|              | estimated    | (1.5 points  |              |
|              | coefficient  | for          |              |
|              | of           | magnitude    |              |
|              | `experience` | and          |              |
|              | correctly.   | statistical  |              |
|              |              | s            |              |
|              |              | ignificance, |              |
|              |              | each)        |              |
+--------------+--------------+--------------+--------------+

## 3) Compute Advertising and Price Elasticities of Demand

Use your model to compute the price elasticity of demand and the
(advertising) budget elasticity of demand. Interpret these elasticities
and assess whether your computed elasticities are consistent with
economic intuition. (12 Points)

#### Solution

First, note that elasticities in a linear demand model are not constant.
Hence, the elasticity depends on the independent
variable's value. Students must pick a sensible value for both variables
to compute the elasticities (advertising budget and price).
A good choice would be to select the average values.

```{r}
elasticity_budget <- coefficients(reg_model_1)["budget_agency"] * mean(df$budget_agency) / mean(df$quantity)
elasticity_budget

elasticity_price <- coefficients(reg_model_1)["price"] * mean(df$price) / mean(df$quantity)
elasticity_price
```

Interpretation of the elasticities:

At the average budget, a 1% increase in advertising budget yields a
0.06% increase in demand. Thus, the value of the advertising elasticity
is 0.06. A positive advertising elasticity makes economic sense because
more advertising should yield higher demand. The value is low but
broadly in line with findings from meta-analytical studies (e.g.,
Sethuraman, Tellis, and Briesch: 0.11)

At the average price, a 1% increase in price yields a 2.29% decrease in
demand. So, the value of the price elasticity is ‑2.29. The size of this
value is plausible because a higher price yields a lower demand. The
value also aligns with findings from meta-analytical studies (e.g.,
Tellis 1988: -1.76; Bijmolt, Herde, and Pieters 2005: -2.62).

+-------------+---------------------+-------------+-------------+
| Step        | Task                | Max. Points | Achieved    |
|             |                     |             | Points      |
+=============+=====================+=============+=============+
| 3-1         | Mentioning that     | 2           |             |
|             | elasticities from a |             |             |
|             | linear demand       |             |             |
|             | function are not    |             |             |
|             | constant.           |             |             |
+-------------+---------------------+-------------+-------------+
| 3-2         | Sensible choice of  | 2           |             |
|             | values at which to  |             |             |
|             | compute the         |             |             |
|             | elasticities (e.g., |             |             |
|             | mean, median,       |             |             |
|             | profit-maximizing   |             |             |
|             | value).             |             |             |
+-------------+---------------------+-------------+-------------+
| 3-3         | Correct computation | 4           |             |
|             | of the two          |             |             |
|             | elasticities.       |             |             |
+-------------+---------------------+-------------+-------------+
| 3-4         | Correct             | 2           |             |
|             | interpretation of   |             |             |
|             | the two computed    |             |             |
|             | elasticities.       |             |             |
+-------------+---------------------+-------------+-------------+
| 3-4         | Correct evaluation  | 2           |             |
|             | of the two computed |             |             |
|             | elasticities'       |             |             |
|             | plausibility        |             |             |
+-------------+---------------------+-------------+-------------+

## 4) Determine the Optimal Price

A sales representative with three years of professional experience and
an engineering degree operates in a sales territory. In addition, the
advertising agency spends a budget of \$2,000, allocating 50% to
telephone and 50% to social media marketing. Determine the optimal price
in this setting and explain the steps you take to arrive at your result.
Assume fixed costs of zero. What is the contribution margin per unit and
the firm's profit? (20 points)

#### Solution

##### **Step 1:** Write the demand function with regression coefficients from the most preferred model

Notation ($equation$ / `code`):

-   $q$ / `q`: quantity sold
-   $q_c$ / `q_c`: quantity sold without price term, constant
-   $p$ / `p`: price
-   $c_v$ / `c_v`: variable costs

$$
\hat{q} = \hat{\beta}_0 + \hat{\beta}_1 \cdot p + \hat{\beta}_2 \cdot experience + \hat{\beta}_3 \cdot engineer +\hat{\beta}_4 \cdot budget\_agency
$$ $$
\hat{q} = \hat{q}_c + \hat{\beta}_1 \cdot p
$$

where $\hat{q}$ is the (expected value of) quantity.\
$\hat{q}_c$ is the expected quantity without considering the price term:

$$
\hat{q}_c = \hat{\beta}_0 +
        \hat{\beta}_2 \cdot experience +
        \hat{\beta}_3 \cdot engineer + 
        \hat{\beta}_4 \cdot budget\_agency
$$

##### **Step 2:** Compute $\hat{q}_c$, the expected quantity without the impact of the price

```{r}
coef <- coefficients(reg_model_1)

q_c <- coef["(Intercept)"] + coef["experience"] * 3 + coef["engineerYes"] * 1 + coef["budget_agency"] * 2000
```

##### **Step 3:** Set up the cost and profit functions

*Cost function*

$$
c(\hat{q}) = c_v \cdot \hat{q} 
     = c_v \cdot (\hat{q}_c + \hat{\beta}_1 \cdot p)
$$

*Profit function*

$$
\pi = p \cdot \hat{q} - c(\hat{q})
$$$$
    = p \cdot (\hat{q}_c + \hat{\beta}_1 \cdot p) - [c_v \cdot (\hat{q}_c + \hat{\beta}_1 \cdot p)]
$$$$
    = p \hat{q}_c + p^2 \hat{\beta}_1 - c_v \hat{q}_c - c_v \hat{\beta}_1 p
$$

##### **Step 4:** Take the first derivative of the profit function with respect to $p$ and set it equal to zero

$$
\frac{\partial \pi}{\partial p} = \hat{q}_c + 2p \hat{\beta}_1 - c_v\hat{\beta}_1  = 0
$$

##### **Step 5:** Rearrange the function to get the optimal price $p^*$

$$
p^* = \frac{1}{2}(c_v - \frac{\hat{q}_c}{\hat{\beta}_1})
$$

##### **Step 6:** Compute the optimal price by inserting the computed values from the above steps

```{r}
c_v <- 200
```

```{r}
p_star <- 0.5 * (c_v - (q_c / coef["price"]))
p_star
```

##### **Step 7:** Compute the profit contribution per unit

```{r}
profit_contribution_unit <- p_star - c_v
profit_contribution_unit
```

##### **Step 8:** Compute the (total) profit

```{r}
q_star <- q_c + coef["price"] * p_star
profit_total <- q_star * profit_contribution_unit
```

The optimal price is \$`r round(p_star, 2)`. The profit contribution per
unit amounts to \$`r round(profit_contribution_unit, 2)`. The firm sells
`r round(q_star)` units of the heater fan, yielding a profit of
\$`r round(profit_total, 2)`.

+-------------+----------------------------+-------------+-------------+
| Step        | Task                       | Max. Points | Achieved    |
|             |                            |             | Points      |
+:============+:===========================+:============+:============+
| 4-1         | Description: Set up demand | 2           |             |
|             | function with regression   |             |             |
|             | coefficients.              |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-2         | Description: Constant      | 2           |             |
|             | demand $\hat{q}_c$         |             |             |
|             | includes all terms from    |             |             |
|             | the regression equation    |             |             |
|             | excluding the price term.  |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-3         | Description: Set up the    | 2           |             |
|             | profit function and insert |             |             |
|             | the demand function into   |             |             |
|             | the profit function.       |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-4         | Description: Take the      | 2           |             |
|             | first derivative of the    |             |             |
|             | profit function with       |             |             |
|             | respect to $p$ and set it  |             |             |
|             | equal to zero.             |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-5         | Description: Rearrange and | 2           |             |
|             | solve for the optimal      |             |             |
|             | price $p^*$.               |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-6         | State the correct formula  | 2           |             |
|             | for the optimal price.     |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-7         | Compute the                | 2           |             |
|             | expected quantity          |             |             |
|             | (constant) without the     |             |             |
|             | price term correctly.      |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-8         | Compute the optimal        | 2           |             |
|             | price correctly.           |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-9         | Compute the profit         | 2           |             |
|             | contribution per unit      |             |             |
|             | correctly.                 |             |             |
+-------------+----------------------------+-------------+-------------+
| 4-10        | Compute the firm's         | 2           |             |
|             | profit correctly.          |             |             |
+-------------+----------------------------+-------------+-------------+

## 5) Impact of Changes on Optimal Prices

Answer the following two sub-questions by ticking the correct answer.

### a)

How does the optimal price change if a sales representative without an
engineering degree works in the sales territory instead of a sales
representative with an engineering degree? (2 points)

The optimal price...

-   increases
-   decreases
-   remains about the same
-   no statement possible

#### Solution

The optimal price remains about the same.

*Explanation (not required):*

Changes in the regression parameter of `engineerYes` cause a parallel
shift of the demand curve (upwards if positive, downwards if negative)
or leave the demand curve unaffected if it is statistically
insignificantly different from zero.

In our case, the parameter estimate of `engineerYes` is statistically
insignificantly different from zero. Hence, we can expect that the
demand curve does not change much, implying that the optimal price
remains the same.

The following computation of the optimal price for a sales
representative without an engineering degree supports this claim:

```{r}
q_c_no_engineer <- coef["(Intercept)"] + coef["experience"] * 3 + coef["budget_agency"] * 2000
p_star_no_engineer <- 0.5 * (c_v - (q_c_no_engineer / coef["price"]))
```

compared to the optimal price *with* an engineering degree

```{r}
p_star
p_star_no_engineer
p_star - p_star_no_engineer
```

The optimal price of a sales representative without an engineering
degree is \$`r round(p_star_no_engineer, 2)`, and with an engineering
degree is \$`r round(p_star, 2)`. The price difference is only
\$`r round(p_star - p_star_no_engineer, 2)`.

Conclusion: The magnitude of the difference between the two optimal
prices is very small and statistically insignificantly different from
zero ($p>0.1$). Hence, the optimal price remains about the same.

### b)

How does the optimal price change if a sales representative with only
one year of professional experience works in the sales territory instead
of a sales representative with three years of professional experience?
(2 points)

The optimal price...

-   increases
-   decreases
-   remains about the same
-   no statement possible

#### Solution

The optimal price decreases

*Explanation (not required):*

Similar to the above exercise, we must consider how the demand function
changes. The demand function changes significantly because the
`experience` regression parameter is statistically significantly
positive.

Hence, a decrease in the level of experience from `3` to `1` (`= -2`)
years causes a parallel downward shift of the demand function. This
change leads to lower demand. Thus, the optimal price decreases.

The following computation of the optimal price with one year of
experience supports this claim.

```{r}
q_c_one_year_experience <- coef["(Intercept)"] + coef["experience"] * 1 + coef["engineerYes"] * 1 +
  coef["budget_agency"] * 2000

p_star_one_year_experience <- 0.5 * (c_v - (q_c_one_year_experience / coef["price"]))
```

compared with the optimal price with three years of experience:

```{r}
p_star
p_star_one_year_experience

p_star_one_year_experience - p_star
```

The optimal price of a sales representative with a one-year experience is
\$`r round(p_star_one_year_experience, 2)`, and with a three-year
experience, \$`r round(p_star, 2)`. The price difference is only
\$`r round(p_star_one_year_experience - p_star, 2)`.

Conclusion: the optimal price decreases by
\$`r -round(p_star - p_star_one_year_experience, 2)`, and the
coefficient on the variable `experience` is statistically significantly
different from zero ($p < 0.01$).

+--------------+--------------+--------------+--------------+
| Step         | Task         | Max. Points  | Achieved     |
|              |              |              | Points       |
+:=============+:=============+:=============+:=============+
| 5-a          | Correct      | 2            |              |
|              | answer       |              |              |
+--------------+--------------+--------------+--------------+
| 5-b          | Correct      | 2            |              |
|              | answer       |              |              |
+--------------+--------------+--------------+--------------+

## 6) Marketing Budget Allocation

The management wants to know whether it should spend the marketing
budget on telephone marketing or social media marketing. Which
recommendation can you give based on your analyses? (2 points)

#### Solution

In this case, no conclusion is possible because the firm always
allocated 50% of the budget to telephone marketing and 50% to social
media marketing in each sales territory. Hence, the two budget variables,
`budget_phone` and `budget_social_media`, are almost perfectly collinear,
making the correct estimation of each variable's effect on the quantity
sold impossible.

| Step | Task           | Max. Points | Achieved Points |
|:-----|:---------------|:------------|:----------------|
| 6    | Correct answer | 2           |                 |

## 7) Performance and Compensation of Sales Representatives

#### a)

Do female sales representatives sell more than non-female sales
representatives? (2 points)

*Answer this question based on your previous results.*

##### Solution

No answer is possible because the data set only includes female sales
representatives.

#### b)

Do business outcomes justify paying sales representatives with an
engineering degree a higher salary than those without an engineering
degree? (2 points)

*Answer this question based on your previous results.*

##### Solution

No, because the expected sold quantity does not differ whether a person
holds an engineering degree (see `engineerYes`). While the estimated
coefficient is positive, it is not statistically significantly different
from zero ($p > 0.1$).

Decrease in estimated sales without an engineering degree:

```{r}
- coef["engineerYes"]
```

Decrease of profit:

```{r}
- coef["engineerYes"] * profit_contribution_unit
```

The profit decreases by
\$`r round(- coef["engineerYes"] * profit_contribution_unit, 2)`.
However, this effect is very small compared to the profit of
\$`r round(profit_total, 2)`. Additionally, the coefficient estimate of
`engineerYes` is not statistically significantly different from zero
($p>0.1$).

#### c)

Do business outcomes justify paying sales representatives with more
professional experience a higher salary than those with less
professional experience? (2 points)

*Answer this question based on your previous results.*

##### Solution

Yes, because the expected quantity increases by
`r round(coef["experience"], 2)` units for each additional year of
experience. The profit contribution per unit is
\$`r round(profit_contribution_unit, 2)`, so
`r round(coef["experience"], 2)` additionally sold units increase the
profit by \$`r round(coef["experience"] * profit_contribution_unit, 2)`
(= `r round(coef["experience"], 2)` \*
\$`r round(profit_contribution_unit, 2)`). Additionally, the estimated
coefficient on the variable `experience` is statistically significantly
different from zero ($p<0.01$).

Thus, business outcomes justify a higher salary for more experienced
sales representatives.

+--------------+-----------------+---------------+--------------+
| Step         | Task            | Max. Points   | Achieved     |
|              |                 |               | Points       |
+:=============+:================+:==============+:=============+
| 7-a          | Correct answer, | 2             |              |
|              | stating that no |               |              |
|              | conclusion is   |               |              |
|              | possible.       |               |              |
+--------------+-----------------+---------------+--------------+
| 7-b          | Correct answer, | 2             |              |
|              | including       |               |              |
|              | stating that    | (0.5 points   |              |
|              | the coefficient | deduction if  |              |
|              | is not          | no level of   |              |
|              | statistically   | significance  |              |
|              | significantly   | is defined)   |              |
|              | different from  |               |              |
|              | zero.           |               |              |
+--------------+-----------------+---------------+--------------+
| 7-c          | Correct         | 2             |              |
|              | conclusion      |               |              |
|              | based on        |               |              |
|              | regression      |               |              |
|              | estimates.      |               |              |
+--------------+-----------------+---------------+--------------+
